Galaxy Zoo: the dependence of the star formation-stellar mass relation on spiral disk morphology

### 2015-02-09 paper/mainsequence_morph.tex
Fixed numbers and fit parameters in Table

\begin{table} 
 \begin{tabular}{@{}lrcrcl}
 \hline
\multicolumn{1}{c}{Sample} &
\multicolumn{1}{c}{$N$} &
\multicolumn{1}{c}{$\alpha$} &
\multicolumn{1}{c}{$\beta$} &
\multicolumn{1}{c}{$\sigma_\alpha$} &
\multicolumn{1}{c}{$\sigma_\beta$} 
\\ 
\hline
\hline						
SF galaxies  & 48405  & $0.72$  & $-7.08$  &  $7.13\times10^{-6}$  & $6.98\times10^{-4}$  \\
\hline
1 arm        & 289    & $0.74$  & $-7.18$  &  $2.70\times10^{-5}$  & $2.69\times10^{-3}$  \\
2 arms       & 5641   & $0.78$  & $-7.69$  &  $3.70\times10^{-5}$  & $3.78\times10^{-3}$  \\
3 arms       & 997    & $0.71$  & $-6.99$  &  $4.49\times10^{-5}$  & $4.65\times10^{-3}$  \\
4 arms       & 285    & $0.71$  & $-7.05$  &  $4.80\times10^{-5}$  & $4.93\times10^{-3}$  \\
5+ arms      & 289    & $0.80$  & $-8.11$  &  $7.54\times10^{-5}$  & $7.53\times10^{-3}$  \\
can't tell   & 2017   & $0.77$  & $-7.72$  &  $4.53\times10^{-5}$  & $4.54\times10^{-3}$  \\
\hline
tight arms   & 3255   & $0.70$  & $-6.99$  &  $1.79\times10^{-3}$  & $1.86\times10^{-1}$  \\
medium arms  & 4578   & $0.77$  & $-7.62$  &  $6.81\times10^{-3}$  & $6.87\times10^{-1}$  \\
loose arms   & 1672   & $0.73$  & $-7.08$  &  $5.81\times10^{-3}$  & $5.76\times10^{-2}$  \\
\hline
barred       & 3199   & $0.75$  & $-7.38$  &  $8.53\times10^{-5}$  & $8.42\times10^{-3}$  \\
unbarred     & 11846  & $0.69$  & $-6.78$  &  $2.91\times10^{-5}$  & $2.89\times10^{-3}$  \\
\hline
merger       & 2978   & --      & $-6.73$  &  --                   & --                   \\
\hline
 \end{tabular}
\caption{Basic properties of the $M_\star-SFR$ linear fit for GZ2 star-forming galaxies. $N$ is the number of galaxies with plurality classifications for spiral arm multiplicity and pitch angles, and at a cutoff of $p_{bar}=0.4$ for barred/unbarred galaxies. {\rr $\alpha$ and $\beta$ are fit according to Equation~\ref{eqn-linearfit} to data weighted by morphological vote fractions for spiral arm multiplicity and pitch angle, and to subsamples split by morphology for barred/unbarred and merging galaxies.}\label{tbl-fits}}
\end{table}

>>>>

\begin{table} 
 \begin{tabular}{@{}lrcrcl}
 \hline
\multicolumn{1}{c}{Sample} &
\multicolumn{1}{c}{$N$} &
\multicolumn{1}{c}{$\alpha$} &
\multicolumn{1}{c}{$\beta$} &
\multicolumn{1}{c}{$\sigma_\alpha$} &
\multicolumn{1}{c}{$\sigma_\beta$} 
\\ 
\hline
\hline						
SF galaxies  & {\rr 48405  }&{\rr $0.72$  }& {\rr $-7.08$  }& {\rr  $7.13\times10^{-6}$  }& {\rr $6.98\times10^{-4}$ } \\
\hline                                                                                                               
1 arm        & {\rr 288    }&{\rr $0.74$  }& {\rr $-7.18$  }& {\rr  $2.70\times10^{-5}$  }& {\rr $2.69\times10^{-3}$ } \\
2 arms       & {\rr 5635   }&{\rr $0.78$  }& {\rr $-7.69$  }& {\rr  $3.70\times10^{-5}$  }& {\rr $3.78\times10^{-3}$ } \\
3 arms       & {\rr 995    }&{\rr $0.71$  }& {\rr $-6.99$  }& {\rr  $4.49\times10^{-5}$  }& {\rr $4.65\times10^{-3}$ } \\
4 arms       & {\rr 283    }&{\rr $0.71$  }& {\rr $-7.05$  }& {\rr  $4.80\times10^{-5}$  }& {\rr $4.93\times10^{-3}$ } \\
5+ arms      & {\rr 286    }&{\rr $0.80$  }& {\rr $-8.11$  }& {\rr  $7.54\times10^{-5}$  }& {\rr $7.53\times10^{-3}$ } \\
can't tell   & {\rr 2002   }&{\rr $0.77$  }& {\rr $-7.72$  }& {\rr  $4.53\times10^{-5}$  }& {\rr $4.54\times10^{-3}$ } \\
\hline                                                                                                               
tight arms   & {\rr 3239   }&{\rr $0.78$  }& {\rr $-7.74$  }& {\rr  $5.50\times10^{-5}$  }& {\rr $5.66\times10^{-3}$ } \\
medium arms  & {\rr 4564   }&{\rr $0.78$  }& {\rr $-7.68$  }& {\rr  $4.16\times10^{-5}$  }& {\rr $4.21\times10^{-3}$ } \\
loose arms   & {\rr 1672   }&{\rr $0.78$  }& {\rr $-7.64$  }& {\rr  $3.21\times10^{-5}$  }& {\rr $3.20\times10^{-3}$ } \\
\hline                                                                                                               
barred       & {\rr 3185   }&{\rr $0.76$  }& {\rr $-7.54$  }& {\rr  $8.97\times10^{-5}$  }& {\rr $8.88\times10^{-3}$ } \\
unbarred     & {\rr 11746  }&{\rr $0.71$  }& {\rr $-6.99$  }& {\rr  $3.39\times10^{-5}$  }& {\rr $3.38\times10^{-3}$ } \\
\hline                                                                                                                
merger       & {\rr 2951   }&     --       & {\rr $-6.79$  }&       --                    &      --                    \\
\hline
 \end{tabular}
\caption{Basic properties of the $M_\star-SFR$ linear fit for GZ2 star-forming galaxies. $N$ is the number of galaxies with plurality classifications for spiral arm multiplicity and pitch angles, and at a cutoff of $p_{bar}=0.4$ for barred/unbarred galaxies. {\rr $\alpha$ and $\beta$ are fit according to Equation~\ref{eqn-linearfit} to data weighted by morphological vote fractions for spiral arm multiplicity and pitch angle, and to subsamples split by morphology for barred/unbarred and merging galaxies.}\label{tbl-fits}}
\end{table}
